Colonies - Compute Continuums across Platforms

### 2023-04-10 paper_2023/paper.tex
wip

Currently, microservices are primarily used to implement large-scale web applications or Internet applications requiring high-availability. It has not yet become a prevalent design principle for workload management or implementation of HPC applications. Instead, simple job scripts are commonly used. J. Represa et al. \cite{GarciaRepresa1740746, GarciaRepresa1640771} explore various challenges associated with developing microservice-based workflow management for industrial automation within the context of the Arrowhead project \cite{delsing2017iot}. The authors conclude that microservice-based workflow technologies are viable for industrial applications, particularly due to their inherent flexibility. The primary contribution of this paper is a comprehensive technical description of how to implement a distributed workflow engine based on microservice principles, extending beyond orchestrating microservices to execute automation tasks within one platform. The vision is to create a distributed architecture where microservices can reside anywhere on the Internet and still function as a cohesive unit to execute cross-platform workflows.

@@

After registration, the executor must connect to the Colonies server and request process assignments of the type \emph{helloworld\_executor}. Note that executor properties, such as the executor type, are not explicitly specified, but rather derived implicitly by the Colonies server from the executor identity, which is derived from the signature generated by executor's the private key. This approach ensures that the executor can only be assigned processes that match its registered capabilities.

@@

When assigned to a process, the executor interprets the metadata stored in the process data structure, including the function name and arguments, and performs some kind of computation such as preprocessing some data or training a neural network. Upon completion, the executor closes the process and sets the output. In the example, the output is set to the the string \emph{helloworld}.

@@

Listing \ref{code:submit} demonstrates how to submit a function specification using the Python SDK and call the \emph{helloworld} function. Note that the executor must complete the process within 100 seconds. If the execution takes longer, the process is reassigned to another executor, and the previosuly executor receives an error upon closure. As discussed in Section \ref{stateless_error_management}, establishing boundaries on computations is critical to achieving robustness and supporting infrastructural changes that may result from DevOps or IT operations.

The Colonies CLI tool can be used to 
\begin{figure}[h]
	\centering
    \includegraphics[scale=0.25]{dashboard1.png}
	\caption{Process information. The timeline makes it possible to follow the execution of process in realtime.}
	\label{fig:dashboard1}
\end{figure}

>>>>

Currently, microservices are primarily used to implement large-scale web applications or Internet applications requiring high-availability. It has not yet become a prevalent design principle for workload management or implementation of HPC applications. Instead, simple job scripts are commonly used. J. Represa et al. \cite{GarciaRepresa1740746, GarciaRepresa1640771} explore various challenges associated with developing microservice-based workflow management for industrial automation within the context of the Arrowhead project \cite{delsing2017iot}. The authors conclude that microservice-based workflow technologies are viable for industrial applications, particularly due to their inherent flexibility. The primary contribution of this paper is a comprehensive technical description of how to implement a distributed workflow engine based on microservice principles, extending beyond orchestrating microservices to execute automation tasks within one platform. The vision is to create a distributed architecture where microservices can reside anywhere on the Internet and still function as a cohesive unit to execute cross-platform workloads.

@@

After registration, the executor must connect to the Colonies server and request process assignments of the type \emph{helloworld\_executor}. Note that executor properties, such as the executor type, are not explicitly specified, but rather derived implicitly by the Colonies server from the executor identity, which is derived from the signature generated by the executor's private key. This approach ensures that the executor can only be assigned processes that match its registered capabilities.

@@

When assigned to a process, the executor interprets the metadata stored in the process data structure, including the function name and arguments, and performs some kind of computation such as preprocessing some data or training a neural network. Upon completion, the executor closes the process and sets the output. In the example, the output is set to the string \emph{helloworld}.

@@

Listing \ref{code:submit} demonstrates how to submit a function specification using the Python SDK and call the \emph{helloworld} function. Note that the executor must complete the process within 100 seconds. The process is reassigned to another executor if the execution takes too long a time. The previous executor then receives an error when trying to send a \emph{close} request. As discussed in Section \ref{stateless_error_management}, establishing boundaries on computations is critical to achieving robustness and supporting infrastructural changes that may result from DevOps or IT operations.

\begin{figure}[h]
	\centering
    \includegraphics[scale=0.23]{dashboard1.png}
	\caption{Process information. The timeline makes it possible to follow the execution of process in realtime.}
	\label{fig:dashboard1}
\end{figure}

Figure \ref{fig:dashboard1} depicts a screenshot of the Colonies dashboard tool, which enables users to monitor the status of processes and executors. The timeline depicted in the figure allows for real-time monitoring of the execution of processes, similar to tracking a physical package sent through a postal service. As previously discussed, it's also possible to subscribe to a process and receive information about its progress, which can be used as another point of integration. For example, sending a notification on Slack or by email if a process fails.

\subsection{Workflows}
A workflow is just a set of processes with dependencies represented as a DAG internally in Colonies. Workflows can either be submitted using SDKs or the Colonies CLI, which supports submission of JSON files. Listening \ref{code:workflow_spec} shows an example of a workflow consisting of four processes, each requiring different types of executors. The management of workflows is entirely handled by Colonies, and each executor executes only processes that are part of the graph for which it is responsible for. This approach significantly reduces the complexity of designing, implementing and operating large-scale AI applications and data pipelines.

\begin{lstlisting}[basicstyle=\small, label=code:workflow_spec, language=json, basicstyle=\small, caption=Example of a workflow]
[ { "nodename": "task_a",
    "funcname": "echo",
    "conditions": { "executortype": "executor_type1", "dependencies": [] } },
  { "nodename": "task_b",
    "funcname": "echo",
    "conditions": { "executortype": "executor_type2", "dependencies": ["task_a"] } },
  { "nodename": "task_c",
    "funcname": "echo",
    "conditions": { "executortype": "executor_type3", "dependencies": ["task_a"] } },
  { "nodename": "task_d",
    "funcname": "echo",
    "conditions": { "executortype": "executor_type4", "dependencies": ["task_b", "task_c"] }
  } ]
\end{lstlisting}

\begin{figure}[h]
	\centering
    \includegraphics[scale=0.23]{dashboard2.png}
	\caption{Screenshot of a workflow in the Colonies dashboard.}
	\label{fig:dashboard2}
\end{figure}

In addition to monitoring processes and executors, the Colonies dashboard can be used to visualize workflows. Figure \ref{fig:dashboard2} illustrates the DAG created when submitting the workflow shown in Listing \ref{code:workflow_spec}. This functionality makes it possible to follow workflow execution progress.
